\begin{thebibliography}{99}
%\bibitem{a}
\bibitem{TDOA-UWB}
\texttt{Janis Tiemann Christian Wietfeld, Scalable and Precise Multi-UAV Indoor Navigation using TDOA-based UWB Localization, 2017 International Conference on Indoor Positioning and Indoor Navigation (IPIN), 18.21 September 2017, Sapporo, Japan}

\bibitem{GraphSLAM}
\texttt{Sebastian Thrun Michael Montemerlo, The GraphSLAM Algorithm with Applications to Large-Scale Mapping of Urban Structures}

\bibitem{GraphSLAMUAV}
\texttt{Arun Annaiyan, Miguel A. Olivares-Mendez, Holger Voos, Real-time graph-based SLAM in unknown environments using a small UAV, 2017 International Conference on Unmanned Aircraft Systems (ICUAS) June 13.16, 2017}

\bibitem{Nanomap}
\texttt{Peter R. Florence1, John Carter1, Jake Ware1, Russ Tedrake1, NanoMap: Fast, Uncertainty-Aware Proximity Queries with Lazy Search over Local 3D Data}

\bibitem{Octomap}
\texttt{A. Hornung, K. M. Wurm, M. Bennewitz, C. Stachniss, and W. Burgard, “Octomap: An efficient probabilistic 3d mapping framework based on octrees,” Auton. Robots, vol. 34, no. 3, pp. 189–206, Apr. 2013. [Online]. Available: http://dx.doi.org/10.1007/ s10514- 012- 9321- 0}

\bibitem{Voxblox}
\texttt{H. Oleynikova, Z. Taylor, M. Fehr, J. Nieto, and R. Siegwart, “Voxblox: Building 3d signed distance fields for planning,” arXiv preprint arXiv:1611.03631, 2016.}

\bibitem{SfMDrone}
\texttt{此村 領, 堀 浩1, 実用性を備えた手のひらサイズ・完全オンボード処理 UAV のための 3 次元自己位置推定手法の提案と全自動飛行の実現, 東京大学工学系研究科航空宇宙工学専攻}

\bibitem{FAST}
\texttt{E. Rosten, R. Porter, and T. Drummond. “Faster and better: A machine learning approach to corner detection.” IEEE Trans. Pattern Analysis and Machine Intelligence, 32:105.119, 2010.}

\bibitem{Brief}
\texttt{M. Calonder, V. Lepetit, C. Strecha, and P. Fua. “Brief: Binary robust independent elementary features.” In European Conference on Computer Vi- sion, 2010.}

\bibitem{DeepDrone}
\texttt{Deepa Kaufmann, Antonio Loquercio, Rene Ranftl, Alexey Dosovitskiy, Vladlen Koltun, Davide Scaramuzza, `Drone Racing: Learning Agile Flight in Dynamic Environments,` University of Zurich and ETH Zurich Intel Labs}

\bibitem{mintraj}
\texttt{Daniel Mellinger,Vijay Kumar, `Minimum Snap Trajectory Generation and Control for Quadrotors,` Shanghai International Conference Center, IEEE International Conference on Robotics and Automation. 2011}

\bibitem{teachue4}
\texttt{Matthias Muller,Vincent Casser, Neil Smith, Dominik L. Michels, Bernard Ghanem, Teaching UAVs to Race: End-to-End Regression of Agile Controls in Simulation, Visual Computing Center at King Abdullah University of Science and Technology}

\bibitem{Honda}
\texttt{横山 利夫,武田 政宣,藤田 進太郎,安井 裕司,Hondaの運転支援および自動運転の現状と今後,本田技術研究所四輪R＆D センター 栃木県芳賀郡芳賀町下高根沢}

\end{thebibliography}
